Dominance Regions for Imaginary $\bfg$-vectors

### 2020-06-11 dominance_regions.tex
Half(?) proof of Lemma 3.4

>>>>

  The Chebyshev polynomials, in particular, allow us to explicitly compute $\phi_{t_i}(\lambda)$ for $\lambda\in\cI$.
  \begin{lemma}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have
    \begin{align*}
      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,-}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,+}\lambda_2);\\
      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,-}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,+}\lambda_2).
    \end{align*}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the case $j=0$ being clear from the definitions.
    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$.
    For $j\ge 0$, using that $(bc-1)u_{2j+1,-}-bu_{2j,-}=u_{2j+3,-}$ and we have
    \[\phi_{t_{2j+2}(\lambda)}=\phi_{t_2}\phi_{t_{2j}}(\lambda)=(u_{2j+3,-}\lambda_1
  \end{proof}
